Survival Analysis of Questions Posted on the iFixit Answers Forum

### 2018-05-03 CSM_poster/main.tex
edits

iFixit's online question and answer forum, \textit{Answers}, features over 120,000 user-asked questions related specifically to device repair. Analysis of question response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how forum design can be improved.

@@

\begin{figure}
\captionsetup{skip=30pt}
\includegraphics[width=1\linewidth]{question}
\caption{Example of a question posted on the forum}
\label{fig1}
\end{figure}

@@

Model was built on the training set and used to predict hazard ratios on the test set

@@

Predicted hazard ratios were entered into separate Cox models; resulting statistics were averaged over each iteration and assessed

@@

Model was fit to the full data and proportional hazards assumption was assessed

@@

\begin{table}[!htbp]
\captionsetup{skip=40pt}
\vspace{3ex}
\begin{tabular}{|r|r|r|r|r|r|r|r|}
  \hline
  & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{C} \\
  \hline
  \textbf{Training} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\
  \textbf{Test}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
  \textbf{Full}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\
  \hline
\end{tabular}
\caption{Performance metrics achieved in cross-validation and for the model fit to the full data (HR: Hazard Ratio, LR: Partial Likelihood Ratio, C: Concordance)}
\label{table:1}
\end{table}

@@

\textcolor{dblue!70}{\ding{228}} Several levels of the device categorization variable violated the proportional hazards assumption

@@

\begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column

\begin{column}{\onecolwid}\vspace{-.6in} % The first column within column 2 (column 2.1)

@@

%----------------------------------------------------------------------------------------
%	INTERPRETING HAZARD
%----------------------------------------------------------------------------------------

\begin{column}{\onecolwid}\vspace{-.6in} % The second column within column 2 (column 2.2)

\end{columns} % End of the split of column 2 - any content after this will now take up 2 columns width

\begin{table}[!htbp]
\captionsetup{width=0.85\textwidth, skip=50pt}
\centering
\begin{tabular}{|L{10cm} L{17.5cm}|c|c|}
  \hline
 \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
  Device Category & Apple Product & 0.93 (0.048) & \textless0.0001 \\ 
                  & Camera & -0.32 (0.090) & \\ 
                  & Electronics & -0.01 (0.078)  & \\ 
                  & Game Console & 0.24 (0.083)  & \\ 
                  & Home & 0.34 (0.070) &  \\ 
                  & Other & -0.13 (0.056)  & \\ 
                  & PC & 0.28 (0.060) &  \\ 
                  & Tablet & -0.16 (0.081)  & \\ 
                  & Vehicle & 0.40 (0.069)  & \\
                  & Android/Other Phone (reference) & --- & \\ \hline
  \multicolumn{2}{|l|}{Weekend} & -0.13 (0.033)  & \textless0.0001 \\ \hline
  \multicolumn{2}{|l|}{Text contains end punctuation} & 0.03 (0.050) & 0.613 \\ \hline
  \multicolumn{2}{|l|}{Text is in all lower case} & -0.18 (0.064) &  0.006 \\ \hline
  \multicolumn{2}{|L{30cm}|}{Title contains terms considered frequently-used among answered questions} & 0.05 (0.042) &  0.260 \\ \hline
  \multicolumn{2}{|L{30cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.28 (0.034)  & \textless0.0001 \\ \hline
  \multicolumn{2}{|L{30cm}|}{Title ends in a question mark} & 0.26 (0.033) &  \textless0.0001 \\ \hline
  \multicolumn{2}{|L{30cm}|}{User edited or added to the question's text after posting it} & 0.30 (0.086)  & 0.001 \\ \hline
  \multicolumn{2}{|L{30cm}|}{User was a member for less than one day before posting} & -0.11 (0.036)  & 0.003 \\ \hline
  \multicolumn{2}{|L{30cm}|}{User made an effort to solve the problem prior to asking the question} & -0.07 (0.036)  & 0.045 \\ \hline
  \multicolumn{2}{|L{30cm}|}{Square root of the average tag frequency} & 2.23 (0.720)  & 0.002 \\ \hline
\end{tabular} 
\caption{Coefficients for predictors in the final model (Continuous predictors fit with restricted cubic splines (text length, average tag length, device name length, ratio of number of newlines to text length) are not shown)} 
\label{table:4}
\end{table}

@@

\textcolor{dblue!70}{\ding{228}} Include more tips to guide users when asking questions

@@

This research was supported by the Bill and Linda Frost fund of the California Polytechnic State University of San Luis Obispo. We also thank iFixit for providing access to the \textit{Answers} data.

>>>>

iFixit's online Q\&A forum, \textit{Answers}, features over 120,000 questions related specifically to device repair. Analysis of question response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times and for how forum design can be improved.

@@

\begin{figure}
\captionsetup{skip=25pt}
\includegraphics[width=1.08\linewidth]{question}
\caption{Example of a question posted on the forum}
\label{fig1}
\end{figure}

@@

Model was built on training sets and used to predict hazard ratios on test sets

@@

Predicted hazard ratios were entered into separate Cox models; resulting metrics were averaged over each iteration and assessed

@@

Model was fit to the full data and proportional hazards (PH) assumption was assessed

@@

\begin{table}[!htbp]
\captionsetup{skip=40pt}
\vspace{2ex}
\begin{tabular}{|r|r|r|r|r|r|r|r|}
  \hline
  & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{C} \\
  \hline
  \textbf{Training} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\
  \textbf{Test}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
  \textbf{Full}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\
  \hline
\end{tabular}
\caption{Performance metrics achieved in cross-validation and for the model fit to the full data (HR: Hazard Ratio, LR: Partial Likelihood Ratio, C: Concordance)}
\label{table:1}
\end{table}

@@

\textcolor{dblue!70}{\ding{228}} Device category violated the PH assumption

@@

@@

\begin{block}{Final Model Coefficients}
\end{block}

\begin{table}[!htbp]
\captionsetup{width=0.85\textwidth, skip=40pt}
\centering
\begin{tabular}{|L{10cm} L{17.5cm}|c|c|}
  \hline
 \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
  Device Category & Apple Product & 0.93 (0.048) & \textless0.0001 \\ 
                  & Camera & -0.32 (0.090) & \\ 
                  & Electronics & -0.01 (0.078)  & \\ 
                  & Game Console & 0.24 (0.083)  & \\ 
                  & Home & 0.34 (0.070) &  \\ 
                  & Other & -0.13 (0.056)  & \\ 
                  & PC & 0.28 (0.060) &  \\ 
                  & Tablet & -0.16 (0.081)  & \\ 
                  & Vehicle & 0.40 (0.069)  & \\
                  & Android/Other Phone (reference) & --- & \\ \hline
  \multicolumn{2}{|l|}{Weekend} & -0.13 (0.033)  & \textless0.0001 \\ \hline
  \multicolumn{2}{|l|}{Text contains end punctuation} & 0.03 (0.050) & 0.613 \\ \hline
  \multicolumn{2}{|l|}{Text is in all lower case} & -0.18 (0.064) &  0.006 \\ \hline
  \multicolumn{2}{|L{30cm}|}{Title contains terms considered frequently-used among answered questions} & 0.05 (0.042) &  0.260 \\ \hline
  \multicolumn{2}{|L{30cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.28 (0.034)  & \textless0.0001 \\ \hline
  \multicolumn{2}{|L{30cm}|}{Title ends in a question mark} & 0.26 (0.033) &  \textless0.0001 \\ \hline
  \multicolumn{2}{|L{30cm}|}{User edited or added to the question's text after posting it} & 0.30 (0.086)  & 0.001 \\ \hline
  \multicolumn{2}{|L{30cm}|}{User was a member for less than one day before posting} & -0.11 (0.036)  & 0.003 \\ \hline
  \multicolumn{2}{|L{30cm}|}{User made an effort to solve the problem prior to asking the question} & -0.07 (0.036)  & 0.045 \\ \hline
  \multicolumn{2}{|L{30cm}|}{Square root of the average tag frequency} & 2.23 (0.720)  & 0.002 \\ \hline
\end{tabular} 
\caption{Not shown: continuous predictors fit with restricted cubic splines (text length, average tag length, device name length, ratio of number of newlines to text length)} 
\end{table}

@@

\vspace{0.75ex}

\textcolor{dblue!70}{\ding{228}} Include tips to guide users asking questions

@@

\textcolor{dblue!70}{\ding{228}} Research was supported by the Bill and Linda Frost fund of California Polytechnic State University, San Luis Obispo. We also thank iFixit for providing access to the \textit{Answers} data.
